Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-09 paper2_JNLS/paper.tex
NM

% Figure: Experimental Spatial Statistics
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/ExpSpatialStats.pdf}
\caption{Wave statistics as they vary in space for several different experiments of different driving amplitudes (see legend). $\etastd$ does not vary significantly crossing the ADC (a), but skewness (b) and kurtosis (c) show a strong response to the ADC. }
\label{ExpSpatialStats}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

>>>>

% Figure: Experimental Spatial Statistics
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/ExpSpatialStats.pdf}
\caption{Wave statistics as they vary in space for several different experiments of different driving amplitudes (see legend). (a)--(c) Standard deviation, skewness, and kurtosis of the surface displacement $\eta$. (d)--(f) The same for surface slope $\eta_x$. A reference wave amplitude is set by $\etastd$ which does not vary significantly crossing the ADC. Skewness and kurtosis of $\eta$, however, show a strong response to the ADC. The surface slope measurements are negatively skewed and also show a large kurtosis downstream of the ADC. }
\label{ExpSpatialStats}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
